### 2018-03-09 paper/background.tex
Add dynamic dependencies example

>>>>

\begin{figure}[h]
\begin{subfigure}[b]{0.90\linewidth}
\centerline{\includegraphics[scale=0.28]{fig/shake-example.pdf}}
\vspace{-1mm}
\caption{Task dependency graph produced after the previous build.}
\vspace{3mm}
\end{subfigure}
\begin{subfigure}[b]{0.90\linewidth}
\centerline{\includegraphics[scale=0.28]{fig/shake-example-rebuild.pdf}}
\vspace{-1mm}
\caption{Since \cmd{docs.txt} is dirty, we rebuild \cmd{release.txt} and
\cmd{release.tar}, discovering a new dependency.}
\end{subfigure}
\caption{Dynamic dependencies example: create \cmd{README} and add it to the
list of release documents \cmd{docs.txt}.\label{fig-shake}}
\end{figure}
